---
title: "Your Representative Report"
author: "Kathy Chen"
date: "May 12, 2019"
output: html_document
---

```{r setup, echo = F}
library(shiny, warn.conflicts = F)
library(knitr, warn.conflicts = F)
source("propublica.R")
source("civic-info.R")
```

## Introduction

This report uses data provided by the [ProPublica API](https://projects.propublica.org/api-docs/congress-api/) and [Google Civic Data API](https://developers.google.com/civic-information/) to compile a report detailing the politicians that represent the resident(s) of: 

`r address`

The following is an **overview** of the respresentatives of the above address including _all levels_ of government.

```{r representative table, echo = F}
kable(rep_table)
```

## State Representatives

Below is an in-depth analysis of the state representatives of the provided address. Specifically, these plots show the breakdown of gender and party affiliation.

```{r rep plots, echo = F}
reps_by_gender
reps_by_party
```

## Representative `r s_full_name`
`r s_full_name` is `r s_age` years old and can be found at [`r s_info$twitter_account`](s_twitter) on Twitter. In the last 20 votes the representative participated in, they agreed with the majority `r percent_agreed`% of the time.